The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities

### 2023-12-15 r_r/letter_to_reviewers.Rmd
the longest yard

**Author response**: The revised Data and Sample section states that "The rationale for different criteria for inclusion across different university types is because these criteria reflected the interest of a foundation that funded the data collection." We agree with Reviewer 1<!--TODO: Is this comment by Reviewer 1 or 2? This is under the level-1 section "Response to Reviewer 2"--> that making comparisons between public and private universities would be more appropriate if we used the same classification method to define the data collection sample for all universities. The revised manuscript now includes a Limitations subsection that describes this limitation and its consequences.

@@

**Author response**: This is an excellent suggestion by Reviewer 1<!--TODO: Is this comment by Reviewer 1 or 2? This is under the level-1 section "Response to Reviewer 2"-->. The new Limitations section in the revised manuscript discusses the drawbacks of a convenience sample.

>>>>

**Author response**: The revised Data and Sample section states that "The rationale for different criteria for inclusion across different university types is because these criteria reflected the interest of a foundation that funded the data collection." We agree with Reviewer 2 that making comparisons between public and private universities would be more appropriate if we used the same classification method to define the data collection sample for all universities. The revised manuscript now includes a Limitations subsection that describes this limitation and its consequences.

@@

**Author response**: This is an excellent suggestion by Reviewer 2. The new Limitations section in the revised manuscript discusses the drawbacks of a convenience sample.

### 2023-12-15 r_r/manuscript_rihe_r_r.Rmd
the longest yard

The High School Longitudinal Survey of 2009 (HSLS) tracks the postsecondary destinations of students who were in ninth grade in 2009. Simple descriptive statistics are eye-opening (Author calculations).^[Analyses consist of students who met the following conditions: completed the 2012 follow-up survey; obtained high school transcript data; and completed the 2016 follow-up survey. The survey weight variable used was W4W1W2W3STU. After weighting, these 14,020 (unweighted) students represent a population of 3.93 million U.S. ninth graders in 2009. Data on college rankings come from the 2020 U.S. News \& World Report *Best Colleges*. Data on high school control come from the HSLS school file and from the Private School Survey.] About 93% of students attended a public high school and 7% attended a private high school, including 3.6% attending a Catholic school, 1.6% attending a nonsectarian school, and 1.8% attending a Christian school. Of public high school students, 5.0% attending a public university ranked in the top 100 by U.S. News and World Report (USNWR) and 1.9% attended a private university ranked in the top 100. Of private high school students, 10.9% attended a top 100 public university and 16.8% attended a top 100 private university. For Catholic school students, 12.8% attended a top 100 public university and 11.7% attended a top 100 private university, while for Christian schools these percentages were 8.2% and 8.2%<!--TODO: Want to double check they're both 8.2%?-->, respectively. However, for nonsectarian private school students, 11.3% attended a top 100 public university and 39.8% attended a top 100 private university. Focusing on the institutional composition of private universities in USNWR top 100, 39.8%<!--TODO: Want to double check this and the previous sentence are both 39.8%?--> attended a private high school (compared to 7% of all high school students who attended a private high school) and 21.2% attended a nonsectarian private high school (compared to 1.6% of all high school students who attended a nonsectarian private high school).

@@

<!--TODO: Supplemental figures \@ref(fig:race-comp-pubu-privhs-pubhs) AND \@ref(fig:race-comp-privu-privhs-pubhs) are now moved to appenidix-->

>>>>

The High School Longitudinal Survey of 2009 (HSLS) tracks the postsecondary destinations of students who were in ninth grade in 2009. Simple descriptive statistics are eye-opening (Author calculations).^[Analyses consist of students who met the following conditions: completed the 2012 follow-up survey; obtained high school transcript data; and completed the 2016 follow-up survey. The survey weight variable used was W4W1W2W3STU. After weighting, these 14,020 (unweighted) students represent a population of 3.93 million U.S. ninth graders in 2009. Data on college rankings come from the 2020 U.S. News \& World Report *Best Colleges*. Data on high school control come from the HSLS school file and from the Private School Survey.] About 93% of students attended a public high school and 7% attended a private high school, including 3.6% attending a Catholic school, 1.6% attending a nonsectarian school, and 1.8% attending a Christian school. Of public high school students, 5.0% attending a public university ranked in the top 100 by U.S. News and World Report (USNWR) and 1.9% attended a private university ranked in the top 100. Of private high school students, 10.9% attended a top 100 public university and 16.8% attended a top 100 private university. For Catholic school students, 12.8% attended a top 100 public university and 11.7% attended a top 100 private university, while for Christian schools these percentages were 8.2% and 8.2%<!--TODO: Want to double check they're both 8.2%?-->, respectively. However, for nonsectarian private school students, 11.3% attended a top 100 public university and an incredible 39.8% attended a top 100 private university.

Focusing on the institutional composition of private universities in USNWR top 100, 39.8%<!--TODO: Want to double check this and the previous sentence are both 39.8%?--> attended a private high school (compared to 7% of all high school students who attended a private high school) and 21.2% attended a nonsectarian private high school (compared to 1.6% of all high school students who attended a nonsectarian private high school).

@@

Finally, Figure X examines the racial composition of private schools visited in the South (upper panel) and the racial composition of public schools visited in the South (lower panel) by public research universities in our sample. Figure X does the same for selective private universities. These figures are motivated by the finding that many universities in our sample visited a large number of private schools in the South, where private school enrollment growth has been the strongest [@RN4504]. For public research universities, Figure X shows that visited Southern private schools tended to enroll dramatically lower shares of Black/Latinx/Native students than visited Southern public schools. This was true for all public universities in our sample, and particularly for UNIVERSITY X, Y, Z. Results for selective private universities in Figure X mirror the results for public research universities. Quite simply, the racial composition of Southern private schools is dramatically different than the racial composition of Southern public schools and these differences are also reflected in schools that received visits. 
<!--TODO: Supplemental figures \@ref(fig:race-comp-pubu-privhs-pubhs) AND \@ref(fig:race-comp-privu-privhs-pubhs) are now moved to appenidix-->
INSERT FIGURES X AND X ABOUT HERE
